Results of two stellar occultations by dwarf planet (1) Ceres

### 2017-08-16 Ceres/Old_versions/CeresV3.tex
mod 2017 ago16

\title[Results of two stellar occultations by Ceres]{Results of two stellar occultations by dwarf planet (1) Ceres}
\author[A. V. Raveendran and A. N. Other]{A. V. Raveendran$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\footnotemark[1]\thanks{}\\
$^{1}$Observat\'orio do Valongo/UFRJ, Ladeira Pedro Ant\^onio 43,
CEP 20.080-090 Rio de Janeiro - RJ, Brazil\\
$^{2}$Observat\'orio Nacional/MCT, R. General Jos\'e Cristino 77,
CEP 20921-400 Rio de Janeiro - RJ, Brazil}
\begin{document}

\date{Accepted . Received ; in original form }

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}

@@

\begin{keywords}
minor planets, asteroids: individual (1, Ceres) - occultations - planets and satellites: fundamental parameters
\end{keywords}

@@

TYC 6833-163-1

@@

The flux of the star in the five occultation chords was obtained from the FITS images with the Platform for Reduction of Astronomical Images Automatically (PRAIA) \citep{2011gfun.conf...85A}. The light curves were normalized to an unocculted star flux. A linear or second-degree polynomial fit was applied to the observed flux before and after the occultation (with exception of INPE).

@@

TYC 865-911-1

>>>>

\title[Results of two stellar occultations by Ceres]{Results of two stellar occultations by dwarf planet (1) Ceres}
\author[A. V. Raveendran and A. N. Other]{A. V. Raveendran$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\footnotemark[1]\thanks{This file has been amended to
highlight the proper use of \LaTeXe\ code with the class file.
These changes are for illustrative purposes and do not reflect the
original paper by A. V. Raveendran.}\\
$^{1}$Indian Institute of Astrophysics, Bangalore 560034, India\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2002}

@@

\begin{keywords}
keywords.
\end{keywords}

@@

@@

The flux of the star in the five occultation chords was obtained from the FITS images with the Platform for Reduction of Astronomical Images Automatically (PRAIA) \citep{Assafin2011}. The light curves were normalized to an unocculted star flux. A linear or second-degree polynomial fit was applied to the observed flux before and after the occultation (with exception of INPE).

@@
